### 2019-04-08 papers/journal/encoding.tex
Minor Fixes in BMC encoding

To specify the stability condition, we use nondeterminism to perform enumeration.
%
%Nondeterminism can be viewed as an oracle that guesses a correct path for a specific $m$ if it exists. 
%
%We then use this path as a witness to ensures that stability is maintained for each outgoing molecule $m$ on every edge $E$.
%
%
Note that the enumeration is done only for an unwinding depth of $w$.
%
The encoding presented below is a simpler version of the implementation. 
\subsubsection{Constraints for stability condition}
%
A path between node $i$ and $j$ in the graph is an $m$-$path_{ij}$ if molecule $m$ is present on edges along that path.
%
%We use {\npath} to represent the required path to encode the stability condition in VTS.
%
%A naive implementation is shown in~\ref{eq:reachbmc1} where 
We use {\npath}$(m, i, j, w)$ to represent the presence of a $m$-$path_{ij}$ of maximum $w$ length.
%there is a edge between $i^{\prime \prime}$ and01
%$(i \neq i^{\prime \prime})$ with $m$ present, and j is $m$-reachable from $i'$ in less than $p-1$ steps.
%
% \begin{align}
%   NOracle (m, i, j, w) = \exists \, path[h1, ..., hn]: \\ 2 \leq |path| \leq  w + 2  \, \land h1 = i \, \land  hn = j \, \land \\ 
%   \bigvee\limits_{k = 1}^{|path|- 1} \bigvee\limits_{q}  E[hk] [hk+1][q][m] 
%   \tag{S1}\label{eq:reach1}
% \end{align}
%The NOracle can be thought of as a disjunction of $m$-path of increment length. 
%
$\npath(m, i, j, w)$ performs enumeration of every $m$-$path_{ij}$ of at most $w$ length. 
%
Starting with exploring $m$-${paths}_{ij}$ of length 1; a direct edge between $i$ and $j$ with molecule $m$ present, until every $m$-${paths}_{ij}$ of length $w-1$ is explored.
%by performing series of node hops till final node destination j is reached.
%Starting with $m$-${paths}_i^j$ of length 1 which is a direct edge between $i$ and $j$ with molecule $m$ present on the edge or performing series of node hops till final node destination j is reached.
%
%|m-path| = 1 \lor  |m-path| = 2 \lor ...  |m-path| = w.     \\
%\bigvee\limits_{l = 1}^{|path| - 1} |m-path| = l
%
\begin{align*}
\npath(m, i, j, w) = \bigvee\limits_{l = 1}^{w-1} (\texttt{Length} (m-path_{ij}) == l)
\end{align*}

@@

\subsubsection{The key difference in the reachability encoding}
The key improvement of the $\fsmt$ search encoding over the $\fbmc$ is the
encoding of reachability.
% which was done using an enumeration of paths.
%
In the $\fbmc$ encoding, reachability is encoded by enumerating all the possible paths using \improve{Do not show up in the encoding}nondeterminism.
%
This encoding is non-optimal in the sense that in the worst case an exponential number of paths needs to be explored.
%
Whereas in the $\fsmt$ encoding, reachability is encoded in two different
ways in constraints $\texttt{Paths}(r)$ and $\texttt{FReach}(d,r')$.
%
The reachability is recursively defined in~$\texttt{FReach}(d,r')$ and has
trivial solutions by making all $r'$s true.
%
However, the trivial solutions are disallowed by constraint~$\texttt{Connected}(r')$ and we find
only the solutions that capture the evidence of non-reachability.
%
On the other hand, we have added the length of paths in our reachability encoding in constraint~$\texttt{Paths}(r)$, which needs relatively more auxiliary variables.
%
This is because constraint~$\texttt{Loop}(r)$ has only positive
occurrences of the reachability variables and if we had defined
$r$s in~$\texttt{Paths}(r)$ without paths,
the circular dependencies in the recursive definitions of $r$s
may have resulted in spurious satisfying assignments that
do not encode reachability.
%
By adding the path length, we break the circular dependencies, the
constraint remains polynomial in size, and satisfying assignments only
correspond to correct reachability.

>>>>

To specify the stability condition, we use nondeterminism to encode the existence of a path. 
%
The nondeterminism can be viewed as a guess of the correct path if it exists. 
%
We then use this path as a witness to ensures that stability is maintained for each outgoing molecule $m$ from an edge $E$.
%
A basic encoding of it using enumeration is shown.
%Nondeterminism can be viewed as an oracle that guesses a correct path for a specific $m$ if it exists. 
%
%We then use this path as a witness to ensures that stability is maintained for each outgoing molecule $m$ on every edge $E$.
%
%
%Only partial enumeration up to an unwinding depth of $w$ is performed.
Note that the enumeration is performed only up to an unwinding depth of $w$.
%
%The encoding presented below uses a nondeterministic path and perform enumeration to find it. 
\subsubsection{Constraints for stability condition}
%
A path between node $i$ and $j$ in the graph is an $m$-$path_{ij}$ if molecule $m$ is present on edges along that path.
%
%We use {\npath} to represent the required path to encode the stability condition in VTS.
%
%A naive implementation is shown in~\ref{eq:reachbmc1} where 
We use {\npath}$(m, i, j, w)$ to represent the presence of a $m$-$path_{ij}$ of maximum $w$ length.
%there is a edge between $i^{\prime \prime}$ and01
%$(i \neq i^{\prime \prime})$ with $m$ present, and j is $m$-reachable from $i'$ in less than $p-1$ steps.
%
% \begin{align}
%   NOracle (m, i, j, w) = \exists \, path[h1, ..., hn]: \\ 2 \leq |path| \leq  w + 2  \, \land h1 = i \, \land  hn = j \, \land \\ 
%   \bigvee\limits_{k = 1}^{|path|- 1} \bigvee\limits_{q}  E[hk] [hk+1][q][m] 
%   \tag{S1}\label{eq:reach1}
% \end{align}
%The NOracle can be thought of as a disjunction of $m$-path of increment length. 
%
$\npath(m, i, j, w)$ performs enumeration of every $m$-$path_{ij}$ of at most $w$ length. 
%
Starting with exploring $m$-${paths}_{ij}$ of length 1; a direct edge between $i$ and $j$ with molecule $m$ present, until every $m$-${paths}_{ij}$ of length $w-1$ is explored.
%by performing series of node hops till final node destination j is reached.
%Starting with $m$-${paths}_i^j$ of length 1 which is a direct edge between $i$ and $j$ with molecule $m$ present on the edge or performing series of node hops till final node destination j is reached.
%
%|m-path| = 1 \lor  |m-path| = 2 \lor ...  |m-path| = w.     \\
%\bigvee\limits_{l = 1}^{|path| - 1} |m-path| = l
%
\begin{align*}
\npath(m, i, j, w) = \bigvee\limits_{l = 1}^{w-1} (\texttt{Length} (m-path_{ij}) == l)
\end{align*}

@@

\subsubsection{The key difference in the reachability encoding}
The key improvement of the $\fsmt$ search encoding over the $\fbmc$ is the
encoding of reachability.
% which was done using an enumeration of paths.
%
In the $\fbmc$ encoding, reachability is encoded by enumerating all the possible paths using nondeterminism.
%
This encoding is non-optimal in the sense that in the worst case an exponential number of paths needs to be explored.
%
Whereas in the $\fsmt$ encoding, reachability is encoded in two different
ways in constraints $\texttt{Paths}(r)$ and $\texttt{FReach}(d,r')$.
%
The reachability is recursively defined in~$\texttt{FReach}(d,r')$ and has
trivial solutions by making all $r'$s true.
%
However, the trivial solutions are disallowed by constraint~$\texttt{Connected}(r')$ and we find
only the solutions that capture the evidence of non-reachability.
%
On the other hand, we have added the length of paths in our reachability encoding in constraint~$\texttt{Paths}(r)$, which needs relatively more auxiliary variables.
%
This is because constraint~$\texttt{Loop}(r)$ has only positive
occurrences of the reachability variables and if we had defined
$r$s in~$\texttt{Paths}(r)$ without paths,
the circular dependencies in the recursive definitions of $r$s
may have resulted in spurious satisfying assignments that
do not encode reachability.
%
By adding the path length, we break the circular dependencies, the
constraint remains polynomial in size, and satisfying assignments only
correspond to correct reachability.
